Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-03 ms.tex
Added some discussion of how Halotools implements the standard HOD

\newcommand{\mvir}{M_{\rm vir}}
\newcommand{\ncen}{N_{\rm cen}}
\newcommand{\nsat}{N_{\rm sat}}

@@

@@

\begin{equation}
\label{eq:ncen}
\langle N_{\mathrm{cen}} \rangle_{M} =
        \frac{1}{2}\left( 1 +
        \mathrm{erf}\left( \frac{\log_{10}M -
        \log_{10}M_{min}}{\sigma_{\log_{10}M}} \right) \right)
\end{equation}

\begin{equation}
\label{eq:nsat}
\langle N_{\rm sat}(M)\rangle = \left( \frac{M - M_0}{M_1} \right)^{\alpha}
\end{equation}

@@

We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters).

>>>>

\newcommand{\mvir}{M_{\rm vir}}
\newcommand{\rvir}{R_{\rm vir}}
\newcommand{\ncen}{N_{\rm cen}}
\newcommand{\nsat}{N_{\rm sat}}

@@

\subsubsection{Simulation}
We use the BolshioP simulation in all analyses (give Citation \& Cosmological Parameters).

@@

\begin{equation}
\label{eq:ncen}
\langle N_{\mathrm{cen}} \rangle(M) =
        \frac{1}{2}\left( 1 +
        \mathrm{erf}\left( \frac{\log_{10}M -
        \log_{10}M_{min}}{\sigma_{\log_{10}M}} \right) \right)
\end{equation}
For every host halo in the catalog we draw a random number from a uniform distribution $\mathcal{U}(0, 1);$ a central galaxy is assigned to each halo whose random number is less than the corresponding value of $\langle N_{\mathrm{cen}} \rangle(M);$ halos with random values exceeding  $\langle N_{\mathrm{cen}} \rangle(M)$ are left devoid of centrals.

We model the distribution $P(\nsat|\mvir)$ to be a Poisson distribution with first moment given by a power law, 
\begin{equation}
\label{eq:nsat}
\langle N_{\rm sat}\rangle(M) = \left( \frac{M - M_0}{M_1} \right)^{\alpha}. 
\end{equation}

@@

Central galaxies in the standard HOD models reside at the halo center, moving with the same velocity as the host halo peculiar velocity. We model the intra-halo spatial distribution of satellite galaxies to be located within $\rvir$ of the halo center, with a spherically symmetric NFW profile \citep{nfw97}. The concentration $c$ of each halo's satellite galaxy profile is taken to be the same as the concentration of the dark matter particles in the halo.\footnote{We set a maximum value of $c=25$ to the NFW concentration, because halos with very large values for the concentration tend to be poorly described by an NFW profile, for example due to a recent merger.}

We model the velocities of satellite galaxies to be a Gaussian whose first moment is the host halo velocity and whose second moment is the solution to the isotropic Jeans equation for an NFW profile \citep{more09b}, 
\begin{equation}
\sigma^{2}_{r}(\tilde{r}|c) = V_{\rm vir}^{2}\frac{c^{2}\tilde{r}(1 + c\tilde{r})^{2}}{g(c)}\int_{c\tilde{r}}^{\infty}{\rm d}y\frac{g(y)}{y^{3}(1 + y)^{2}}, 
\end{equation}
where $\tilde{r} = r/\rvir$ and $g(y) = \rm{ln}(1+y) - y / (1+y).$
